---
title: "Hormone_analysis_report"
author: "MM"
date: "10-11-2020"
output: html_document
Bibliography: literature/Bibliopraghy.bib
---

# Analysis of hormone project

This script analysze the dataset of the hormone experiment performend on
It contains

Here is a reference to a paper [@misc{Schmid-Grendelmeier2001]

## 1. Import libraries
Install the packages and load in the libraries

```{r, warning=FALSE}
# install.packages("ggplot2")
library(ggplot2)
```


## 2. Data analysis

### 2.1 Import samples
```{r, results='hide'}
Hormone <- read.csv2("data/20201110_Hormone.csv")
names(Hormone)[3] <- "Concentration"
Hormone
```

```{r}
summary(Hormone)
```

### 2.2 Create figures
Create plot effect of drup A ad B on concentration of substance X measured in blood. 

```{r, fig.cap="Results",fig.width=3, fig.height=1.5}
ggplot(Hormone, aes(Drug,Concentration)) +
	          stat_summary(fun=mean,geom="bar") +
		              stat_summary(fun.data=mean_cl_normal,geom="errorbar",
					                                           width=0.25) + geom_point() +
  coord_flip()

```

## 3. Discussion
There is a clear influence present.

## 4. Conclusion


## 5. Final notes
This report was created with r version: `r getRversion()`. The following packages were used for the analysis. 

```{r}
sessionInfo()
```












